### 2021-08-31 paper.Rmd
notation explanation of geodesic added

A tour path, that is a sequence of projections, can be generated by geodesic interpolation between a set of target planes (Figure \ref{fig:tour-path}). Different methods for choosing target planes provide different tour paths. The grand tour [@Asimov1985-xr] is generated using randomly selected targets. A guided tour [@Cook1995-ae] generates targets as a sequence of interesting projections $A_i$ by applying projection pursuit optimization on a predefined criteria $c(\cdot)$ of ``interestingness'' of a projection, $argmax_A c(XA)$. A local tour (available originally in [@Buja1986-la] rocks back and forth from a particular plane $A$ to randomly chosen targets $A_i$ in a small neighborhood $\{A_j |\; d(A_j, A) < \epsilon \}$. A little tour (available originally in [@Buja1986-la] navigates through all of the coordinate planes, for example, for 2D projections $\{A_{ik} = 1, A_{lj} = 1, \forall i, j, k, l = 1, ..., p; i\neq j\}$.

@@

The smooth progression in the tour path is due to geodesic interpolation between the target planes. This takes into consideration two important aspects: (1) it maintains the orthonormality of the projection bases, (2) contains all the rotation to be between planes, not a particular basis in any plane. The first is clearly important because it ensures that we are looking at low-dimensional projections of the data always. The latter is harder to explain, but really important from a visual perspective. It stops any within-plane spin, and could be considered stabilizing the view. A more detailed explanation of this can be found in @Buja2005-cx.

@@

## Basic Interactions

@@

## Manual Tours {#tours}

@@

## Model Visualization

>>>>

A tour path, that is a sequence of projections, can be generated by geodesic interpolation between a set of target planes (Figure \ref{fig:tour-path}). Different methods for choosing target planes provide different tour paths. The grand tour [@Asimov1985-xr] is generated using randomly selected targets. A guided tour [@Cook1995-ae] generates targets as a sequence of interesting projections $A_i$ by applying projection pursuit optimization on a predefined criteria $c(\cdot)$ of ``interestingness'' of a projection, $argmax_A c(XA)$. A local tour (available originally in @Buja1986-la rocks back and forth from a particular plane $A$ to randomly chosen targets $A_i$ in a small neighborhood $\{A_j |\; d(A_j, A) < \epsilon \}$. A little tour (available originally in @McDonald1982-ht navigates through all of the coordinate planes,  e.g. in 2D this would correspond to all elements of $A$ are 0 except for one element in each column, $(A_{i1} = A_{j2} = 1, A_{k1} = A_{k2} = 0, ~~i, j, k = 1, ..., p, ~~i\neq j \neq k)$.

@@

The smooth progression in the tour path is due to geodesic interpolation between the target planes. This takes into consideration two important aspects: (1) it maintains the orthonormality of the projection bases, (2) contains all the rotation to be between planes, not a particular basis in any plane. The first is clearly important because it ensures that we are looking at low-dimensional projections of the data always. The latter is harder to explain, but really important from a visual perspective. It stops any within-plane spin, and could be considered stabilizing the view. A geodesic interpolation between two planes is obtained by (1) using singular value decomposition of $A_1^T A_2$ to compute the $d$ smallest angles between the two planes, (2) dividing these angles into small intervals, (3) generating intermediate projection planes by rotating the initial basis $A_1$ by these angle increments. A more detailed explanation of this can be found in @Buja2005-cx.

@@

## Basic interactions

@@

## Manual tours {#tours}

@@

## Model visualization
